|

### 2021-07-01 paper/manuscript.Rmd
add paper citation

---
title             : "How young children integrate information sources to infer the meaning of words"
shorttitle        : "Rational information integration in children"

>>>>

---
title: |
    | Published as:
    | Bohn, M., Tessler, M. H., Merrick, M., & Frank, M. C. (2021). How young children integrate information sources to infer the meaning of words. Nature Human Behaviour. https://doi.org/10.1038/s41562-021-01145-1
    | 
    | 
    | 
    | How young children integrate information sources to infer the meaning of words

shorttitle        : "Rational information integration in children"
